LAGOS lake depth

### 2020-03-23 figures/01_geometry.Rmd
theme cleanup

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

gg_scatter_reservoir <- ggplot(data = dplyr::filter(
  st_drop_geometry(dt), !is.na(reservoir_class))) + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class)) +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")
```

@@

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5}
theme_opts <- theme(legend.position = "none")

@@

cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts,
                     gg_slope_shape +
                       theme_opts,
                     gg_slope_reservoir + 
                       theme(axis.title.y = element_blank()) +
                       theme_opts, 
                     rel_widths = c(1, 0.93, 1, 1)), 
  legend_panel, rel_widths = c(1, 0.2)
)
```

>>>>

gg_scatter_shape <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  dplyr::arrange(desc(factor(shape_class, 
                        levels = c("neither", "concave", "convex")))) %>%
  ggplot(aes(x = dist_deepest, y = dist_viscenter, color = shape_class)) + 
  geom_point() +
  # geom_abline(aes(intercept = 0, slope = 1)) +
  labs(color = "") +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")

gg_scatter_reservoir <- st_drop_geometry(dt) %>%
  dplyr::filter(!is.na(reservoir_class)) %>%
  dplyr::filter(dist_viscenter >= dist_deepest) %>%
  ggplot() + 
  geom_point(aes(x = dist_deepest, y = dist_viscenter, color = reservoir_class)) +
  scale_color_discrete(labels = c("NL     ", "Res")) + 
  # geom_abline(aes(intercept = 0, slope = 1)) +
  xlab("Deepest point distance (m)") +
  ylab("Visual center distance (m)")
```

@@

```{r 01_geometry_grid, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=5.5, fig.height=4.2}
theme_opts <- cowplot::theme_cowplot() + 
  theme(legend.position = "none", 
        axis.text = element_text(size = 10), 
        axis.title = element_text(size = 11))

@@

cowplot::plot_grid(
  cowplot::plot_grid(
  cowplot::plot_grid(gg_scatter_shape + 
                       labs(color = "") +
                       # theme(axis.title.x = element_blank()) +
                       theme_opts,
                     gg_scatter_reservoir + 
                       labs(color = "") +
                       theme(#axis.title.x = element_blank(), 
                             axis.title.y = element_blank()) +
                       theme_opts, 
                     ncol = 2),
  cowplot::plot_grid(ggplot() + geom_blank() + 
                       theme_opts + theme(axis.line = element_blank()), 
                     gg_slope_shape +
                       theme_opts,
                     gg_slope_reservoir + 
                       theme(axis.title.y = element_blank()) +
                       theme_opts,
                     ncol = 3, rel_widths = c(0.08, 1, 1)), 
                     rel_widths = c(1, 1), nrow = 2), 
  legend_panel, rel_widths = c(1, 0.12)
)
```
